---
title: "Animation Movies Analysis"
---

## Background

Animation movies, a vibrant blend of art and storytelling, have evolved significantly since their inception. The journey began with short, silent cartoons in the early 20th century, gradually transforming into feature-length films by the 1930s, marked by the release of Disney's "Snow White and the Seven Dwarfs." Over the decades, the advancement of computer-generated imagery (CGI) revolutionized the industry, beginning with Pixar's "Toy Story" in 1995, the first fully computer-animated feature film. Animation styles have diversified, embracing traditional hand-drawn, stop-motion, and digital techniques, appealing to a broad audience beyond just children. Today, animation movies are celebrated for their complex storytelling, intricate visuals, and the ability to explore a wide range of themes, making them a beloved genre worldwide.

## Aim

My analysis of animation movies aims to identify trends over time, such as shifts in rates of popularity based on its released year, and to evaluate the economic aspects, including budget vs. revenue analysis, to determine what types of animation movies are most commercially successful.

## About Data Set

The data set that I am using for my analysis is from Kaggle by Ayush Chandra Maurya titled: "Animation movies". The dataset contains detailed information of animation movies scraped from the TMDB API. The following is a glimpse of the data set:

```{r, eval=TRUE,echo=FALSE}
library(tidyverse)
```

```{r, eval=TRUE,echo=FALSE}
data <- read.csv("Animation_Movies.csv")
glimpse(data)

```
